Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-11 Supplemental-Material-B-Annotated-Analysis.Rmd
rendered

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
         "sessioninfo", "tibble", "pander", "devtools",
         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", 
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

@@

  dtWorker$munge <- between

@@

```{r newVarsStudents}
df <-

@@

# order time
  # move this here? 
  # date.period.order <- unique(raw$dat.daily$date_period)
  date.period.order <- .GlobalEnv$date.period.order # <- @Max: Do you still need this? Order should be fine natively from FormR

  df$TID <- factor(df$date_period, levels = date.period.order)
  df$TIDnum <- as.numeric(df$TID) #get numeric TID

  # check whether time ordering worked
  df_ordered <- df %>%
    arrange(PID, TID) #%>%
    #View()

@@

# ------------------------------------------------------------------------------------------------------------- 
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
source("lib/fun.panel.R")
# Relatedness
  .GlobalEnv$pairs.panels.new(df[c("RelatednessSelf","RelatednessOther")], 
                              labels = c("I shared information about myself.", "X shared information about themselves."))
  df$RelatednessInteraction <- rowMeans(df[c("RelatednessSelf","RelatednessOther")], na.rm=T)
  df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <- NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
  df$Relatedness <- rowMeans(df[,c("RelatednessInteraction", "RelatednessNoInteraction")], na.rm=T)
# Pro-Sociality
  df$ProSo <- rowMeans(df[,c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm=T)
# Anti-Sociality
  df$AntiSo <- rowMeans(df[,c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm=T)

# ------------------------------------------------------------------------------------------------------------- 
#                                 Create Time Variables
# -------------------------------------------------------------------------------------------------------------
createTimeDf <- function(tmp) {
# make dataframe for all variables that need t-1
# @Max: LAGS AREN'T REALLY MEANINGFUL BECAUSE OF THE TIME INTERVAL DIFFERENCES, WE WILL DO THIS IN DSEM (MPLUS).
  tmp <- data.frame(KeyNeedFullfillment = tmp$KeyNeedFullfillment,
                    ProSo = tmp$ProSo,
                    AntiSo = tmp$AntiSo,
                    AttitudesDutch = tmp$AttitudesDutch)
    length <- ncol(tmp) # get the length of tmp for later renaming of columns

  # use dplyr to create time series
    tmp <- tmp %>% mutate_each(funs(lag(.,1))) %>% cbind(tmp, .)
    colnames(tmp)[(length+1):ncol(tmp)] <- paste(colnames(tmp)[1:length], "Lag1", sep = "") #rename after specific length (add one so new columns get renamed after that)
  tmp
}

# split df per participants and run function
  PP <- split(df, df$PID)
  PP <- lapply(PP, createTimeDf); rm(createTimeDf)

# add variables back to df
  tmp <- do.call(rbind.data.frame, PP)
    colnames(tmp) <- paste(colnames(tmp), "Calc", sep = "")
df <- cbind(tmp, df);rm(tmp)

# ------------------------------------------------------------------------------------------------------------- 
#                                 Add Variables related to interaction partner
# -------------------------------------------------------------------------------------------------------------

# create function for later lapply
createIntPartDf <- function(inp) {

@@

    tmp$CC2 <- recode(tmp$CC, "'SOMEONE ELSE' = NA")
    tmp$CC2 <- ifelse(tmp$CC == 1 | tmp$CC == "SOMEONE ELSE", as.character(tmp$NewName), as.character(tmp$CC2)) 
    # maybe add [[:space:]]\b to remove space before word boundary or ^[[:space:]] to remove space in the beginning of a string
    tmp$CC2 <- gsub("^[[:space:]]", "", tmp$CC2)
    tmp$NewName <- gsub("^[[:space:]]", "", tmp$NewName)

@@

# add variables back to df
  remergePP <- do.call(rbind.data.frame, PP)
    colnames(remergePP) <- paste(colnames(remergePP), "_Calc", sep = "")
df <- cbind(remergePP, df);rm(remergePP)
print("Test whether newly calculate df and old df have the same order:")
print(table(as.character(df$CC_Calc) == as.character(df$CC)))
print("If we also add the NAs we get the exact number:")
print(sum(is.na(df$CC_Calc))+table(as.character(df$CC_Calc) == as.character(df$CC)))

# ------------------------------------------------------------------------------------------------------------- 
#                                 Center Relevant Variables
# -------------------------------------------------------------------------------------------------------------
  # center within participant
  # @Max: I removed the lagged variables so we can do it proberly in MPlus
    df$ProSo_c <- ave(df$ProSoCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
    #df$ProSoLag1_c <- ave(df$ProSoLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
    df$AntiSo_c <- ave(df$AntiSoCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
    #df$AntiSoLag1_c <- ave(df$AntiSoLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
    df$KeyNeedFullfillment_c <- ave(df$KeyNeedFullfillmentCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
    #df$KeyNeedFullfillmentLag1_c <- ave(df$KeyNeedFullfillmentLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))

    df$closeness_c <- ave(df$closeness_Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))

# variancec
  df$var.AntiSo <- ave(df$AntiSo, df$PID, FUN=var)

# send back to global environment
  .GlobalEnv$df.full = df

>>>>

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
         "sessioninfo", "tibble", "pander", "devtools", "mada",
         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", 
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

@@

  dtWorker$full <- between

@@

```{r newVarsStudents}
df <- dtStudents$clean

@@

# order time
  df$TID <- factor(df$date_period, levels = unique(dtStudents$raw.daily$date_period))
  df$TIDnum <- as.numeric(df$TID) #get numeric TID

  # check whether time ordering worked
  df <- df %>%
    arrange(PID, TID) #%>%
    #View()

@@

# ------------------------------------------------------------------------------------------------------------- 
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
  pairs.panels.new(df[c("RelatednessSelf","RelatednessOther")], 
                              labels = c("I shared information about myself.", "X shared information about themselves."))
  df$RelatednessInteraction <- rowMeans(df[c("RelatednessSelf","RelatednessOther")], na.rm=T)
  df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <- NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
  df$Relatedness <- rowMeans(df[,c("RelatednessInteraction", "RelatednessNoInteraction")], na.rm=T)
# Pro-Sociality
  df$ProSo <- rowMeans(df[,c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm=T)
# Anti-Sociality
  df$AntiSo <- rowMeans(df[,c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm=T)

# ------------------------------------------------------------------------------------------------------------- 
#                                 Add Variables related to interaction partner
# -------------------------------------------------------------------------------------------------------------
# create function for later lapply
createIntPartDf <- function(inp) {

@@

    tmp$CC2 <- recode(tmp$CC, 'SOMEONE ELSE' = "NA")
    tmp$CC2 <- ifelse(tmp$CC == 1 | tmp$CC == "SOMEONE ELSE", as.character(tmp$NewName), as.character(tmp$CC2)) 
    # maybe add [[:space:]]\b to remove space before word boundary or ^[[:space:]] to remove space in the beginning of a string
    tmp$CC2 <- gsub("^[[:space:]]", "", tmp$CC2)
    tmp$NewName <- gsub("^[[:space:]]", "", tmp$NewName)

@@

# add variables back to df
  remergePP <- do.call(rbind.data.frame, PP)
    colnames(remergePP) <- paste(colnames(remergePP), "_Calc", sep = "")
df <- cbind(df, remergePP);rm(remergePP)
writeLines("Test whether newly calculate df and old df have the same order:")
print(table(as.character(df$CC_Calc) == as.character(df$CC)))
writeLines("If we also add the NAs we get the exact number:")
print(sum(is.na(df$CC_Calc))+table(as.character(df$CC_Calc) == as.character(df$CC)))

# ------------------------------------------------------------------------------------------------------------- 
#                                 Center Relevant Variables
# -------------------------------------------------------------------------------------------------------------

df <- df %>%
  group_by(PID) %>% 
  mutate(
    KeyNeedFullfillment.cm = mean(KeyNeedFullfillment, na.rm = TRUE), # cluster mean (mean of PP)
    KeyNeedFullfillment.cwc = KeyNeedFullfillment - KeyNeedFullfillment.cm, # cluster mean centered (within PP centered)
    closeness.cm = mean(closeness_Calc, na.rm = TRUE),
    closeness.cwc = closeness_Calc - closeness.cm
    ) %>%  
  ungroup()

# store
  dtStudents$full = df
```
